Knowledge Representation for Service Robots: Supply and Demand

### 2012-05-16 krs-survey.tex
Add mentions of GOLOG and derivatives

@@

\paragraph{Diagnosis}: this corresponds to the ability to rewind on past events
in case of failure to provide possible explanation. This can be seen as the
temporal reverse of the projection task.

@@

>>>>

We have also chosen not to include the GOLOG language and its
derivatives~\cite{Levesque1997, Ferrein2008, Gspandl2011} in this survey. While
several implementations on robots, including service robots, do exist, the
focus of this language is on representation and reasoning about actions and
situations, and the link with symbolic, abstract knowledge is not explicit.

@@

\paragraph{Diagnosis}: this corresponds to the ability to rewind on past events
in case of failure to provide possible explanation. This can be seen as the
temporal reverse of the projection task. Because of their modelisation of
situations as an history of actions, derivatives of the GOLOG logic programming
languages are a good example of diagnosis tasks integrated to the knowledge
representation system~\cite{Gspandl2011}.

@@

The GOLOG~\cite{Levesque1997} language and its derivatives (like {\sc
ReadyLOG}~\cite{Ferrein2008} and {\sc IndiLOG}~\ref{Gspandl2011}) propose
implementations of the situation calculus focused on robotic applications.
